Scalar Items in Embedded Position: {A}n Experimental Revisit

### 2012-07-04 text/paper/paper.tex
paper micha version on critique of previous studies and motivation of our own

\citet{ChemlaSpector2010:Experimental-Ev} also took issue with
\citeauthor{GeurtsPouscoulous2009:Embedded-Implic}'s design, arguing
that, firstly, the pictorial material used in
\citeauthor{GeurtsPouscoulous2009:Embedded-Implic}'s study was unduly
difficult; that, secondly, these pictures also may have failed to make
the local reading sufficiently relevant; and that, thirdly, the
restriction to a categorial choice (whether the sentence fits the
picture of not) may induce a bias against non-preferred readings in
cases where candidate readings stand in entailment relations
\citep[c.f.][for this latter
criticism]{Sauerland2010:Embedded-Implic}. To meet these potential
problems, \citet{ChemlaSpector2010:Experimental-Ev} presented subjects
with pictorial material like that in Figure~\ref{fig:Chemla-Spector},
which was assumed to be easier to assess and better at highlighting
the relevance of the local readings. Albeit in a different format, the
pictures used by \citeauthor{ChemlaSpector2010:Experimental-Ev} were
all different instantiation of the situation types in
Figures~\ref{fig:AS-distinguishing-pics} and
\ref{fig:ES-distinguishing-pics}. Additionally, subjects were asked,
not for categorial judgements, but for \mymark{graded judgements}:
subjects could freely click on a scale, as shown in
Figure~\ref{fig:Chemla-Spector}, to indicate how much they considered
a picture fitting for a given sentence \citep[c.f.][for more on this
method]{Chemla2009:Presuppositions}.

\begin{figure}[t]
  \centering
      \includegraphics[scale=0.35]{../pictures/paper/Chemla_Spector_2010_Critical_AE.png}\\
      \includegraphics[scale=0.35]{../pictures/paper/Chemla_Spector_2010_RatingBar.png}
        \caption{Example of critical trial for \as-condition by
          \citeauthor{ChemlaSpector2010:Experimental-Ev}'s
          (\citeyear{ChemlaSpector2010:Experimental-Ev})}
  \label{fig:Chemla-Spector}
\end{figure}

\citeauthor{ChemlaSpector2010:Experimental-Ev} hypothesized that the
degree to which a sentence was rated acceptable is proportional to the
number of available true readings. Observed averaged clicking
positions are shown in Figure~\ref{fig:Chemla-Spector-Results}.
%
\begin{figure}
  \centering
  \subfloat[][\as-condition]{
    \label{fig:CS-Results-as}
        \includegraphics[width=5.5cm]{../pictures/paper/Chemla_Spector_2010_Results_AE.png}
  }
  \subfloat[test][\es-condition]{
    \label{fig:CS-Results-es}
    \includegraphics[width=5.5cm]{../pictures/paper/Chemla_Spector_2010_Results_GE.png}
  }
  \caption{Results from
    \citeauthor{ChemlaSpector2010:Experimental-Ev}'s
    (\citeyear{ChemlaSpector2010:Experimental-Ev}) study}
  \label{fig:Chemla-Spector-Results}
\end{figure}
%
According to \citeauthor{ChemlaSpector2010:Experimental-Ev}, the
crucial piece of evidence for the availability of local readings for
\as-sentences is that these sentences yielded higher graded
acceptability scores for the strong situation than for the weak
situation (although these differ only with respect to the truth value
of the local reading). In a similar way, evidence for the availability
of the local reading for \es-sentences comes from the difference
between the local and the literal situation. Strikingly, in the latter
case, the \es-sentences received an average of 73\% acceptability in
the local situation although the literal and global readings are false
in this case.

@@

Summing up so far, three previous studies have presented different
pieces of evidence concerning putative local readings. G\&P's results
suggest that local readings are not available, because they do not
affect a categorical truth-value judgments in a picture-verification
task. On the other hand, C\&D's and C\&S's design was suggested to be
sensitive enough to reveal effects of local readings: either by a
choice of the situation that better befits a given sentence (C\&D), or
by a graded truth-value judgment (C\&S).

To account for all of the available data in conjunction, it could be
hypothesized along with C\&D and C\&S that local readings are
available, but so dispreferred they do not affect simple
\emph{categorical} truth-value judgements. This, however, does not
seem to be the case, as revealed by a pilot study of ourselves. We
tried to replicate G\&P's results, using a simple categorial
truth-value judgement task on pictures that were exactly like those in
Figures \ref{fig:AS-distinguishing-pics} and
\ref{fig:ES-distinguishing-pics}. Test sentences were German
cleft-constructions as in (\ref{bsp:AS-K1}) and
(\ref{bsp:ES-K1}).\fn{We concede that these cleft-constructions might
  unduly emphasize potential local readings, but that is not
  essential, because the main issue we are trying to address here is
  whether putative local readings \emph{could} affect categorical
  truth-value judgements.}
\begin{exe}
\ex \gll F\"{u}r \mymark{jedes} dieser Kinder gilt: es
  mag \mymark{einige} dieser Speisen. \label{bsp:AS-K1}\\
  For every {of these} children {it holds} it likes some {of
    these} dishes.\\
  For all of these children it holds that it likes some of these dishes.
\end{exe}
\begin{exe}
\ex \gll F\"{u}r \mymark{genau} \mymark{eines} dieser Kinder gilt: es
  mag \mymark{einige} dieser Speisen. \label{bsp:ES-K1}\\
  For exactly one {of these} children {it holds} it likes some {of
    these} dishes.\\
  For exactly one of these children it holds that it likes some of these dishes.
\end{exe}
60 native German speakers (40 female, mean age: $24$, ranging between
$20$ and $40$) participated in this pilot. Participants were na\"ive
to the purpose of the study and were paid \euro{10}
compensation.\dn{We should expand on the method in an appendix}

Mean acceptance rates for our target
sentences were (see also Figure~\ref{fig:Bars-K1}):
\begin{center}
  \begin{tabular}{ccccccccc}
    \multicolumn{4}{c}{\as-sentences} &&
    \multicolumn{4}{c}{\es-sentences}     \\ \cmidrule(r){1-4} \cmidrule(r){6-9}
    false & literal & weak & strong && false & local & literal & all
    \\ \midrule 
    .9 & 72 & 79 & 90 && .8 & 20 & 71 & 93 
  \end{tabular}
\end{center}
Two observations are of interest here. Firstly, unlike G\&P, we
observed \emph{false}-judgements in the \as-weak condition, as well as
\emph{true}-judgements in the \es-local condition. Secondly, the
observed difference between the \as-weak and the \as-strong
conditions, on the one had, and the \es-false and the \es-local
condition, on the other hand, both reached significance.\dn{spell out
  in appendix}

\begin{figure}[]
\centering
\subfloat[\as-sentences]{
\includegraphics[width=5.5cm]{../pictures/paper/JudgmentsAllSomeBars.pdf}
\label{fig:EABars}
}
\subfloat[\es-sentences]{
\includegraphics[width=5cm]{../pictures/paper/JudgmentsExactlySomeBars.pdf}
\label{fig:EEBars}
}
\caption{Means of \emph{true}-judgments in our pilot study}
\label{fig:Bars-K1}
\end{figure}

The perhaps most obvious explanation for these observed patterns is
that local readings \emph{are} available and \emph{can} have an effect
even on categorical truth-value judgements. However, we believe that
this interpretation of the data is problematic for reasons already
addressed also by \citet{ChemlaSpector2010:Experimental-Ev} and, more
recently, \citet{Tielvan-Tiel2012:Embedded-Scalar}. The problem is
that the present variants of truth-value judgment tasks all run risk
of conflating evidence about the availability or preference of
readings with properties of the pictorial material that are
independent of the reading to be assessed. This problem affects all of
the studies covered above, to some degree or other, because it follows
almost directly from the nature of the phenomenon under investigation
and therefore seems nearly impossible to avoid.

To illustrate the potential conflation, consider a sentence like
(\ref{bsp:EA}), which is a ``global alternatives'' to an \es-sentence,
with a universal quantifier where an \es-sentence has scalar
\emph{some}.
\begin{exe}
\ex \gll F\"{u}r \mymark{genau} \mymark{eines} dieser Kinder gilt: es
  mag \mymark{jede} dieser Speisen. \label{bsp:EA}\\
  For exactly one {of these} children {it holds} it likes all {of
    these} dishes.\\
  For exactly one of these children it holds that it likes all of these dishes.
\end{exe}
Sentence like (\ref{bsp:EA}) are literally true in both of the
situations given in Figure~\ref{fig:EA-distinguishing-pics}, but these
situations differ in the truth value of the corresponding
\es-sentence. Our pilot study revealed a difference in acceptability,
but a curious one. The sentence was judged \emph{true} in 90.34\% of
the cases for the situation in Figure~\ref{fig:global-EA} and in
98.34\% in situation \ref{fig:literal-EA}. The observed difference is
significant ($t = -3.8259$, $df = 322.375$, $p < 0.001$). This is a
curious finding, because, from the point of view of implicature
calculation, the only thing that could plausibly explain this
acceptability difference is the presence of a global implicature,
resulting from the negation of the corresponding \es-sentence. But
such a putative global implicature would be true in the
situation~\ref{fig:global-EA}, but false in the
situation~\ref{fig:literal-EA}. Consequently, the observed difference
in acceptability cannot be explained simply in terms of the hypothesis
of \citet{ChemlaSpector2010:Experimental-Ev} that acceptability is
proportional to the number of available true readings. Rather some
feature of the pictorial material that is independent of the putative
readings under scrutiny does affect truth-value judgements, even
categorical ones.

\citet{ChemlaSpector2010:Experimental-Ev} acknowledge the possibility
that the \emph{typicality} of a picture may affect graded truth-value
judgements. Stronger still, they show that graded judgments of
\as-sentences differ significantly for different instantiations of the
conditions in \ref{fig:AS-distinguishing-pics}, that differ in the
amount of connections, but not so that they would alter the assignment
of truth-values to candidate
readings. \citeauthor{ChemlaSpector2010:Experimental-Ev} suggest that
typicality of the pictorial material can account for these
differences, but submit that this does not explain away the effect of
the local reading. This is disputed by
\citet{Tielvan-Tiel2012:Embedded-Scalar}, who demonstrates that all of
\citeauthor{CliftonDube2010:Embedded-Implic}'s and
\citeauthor{ChemlaSpector2010:Experimental-Ev}'s data on \as-sentences
can be explained as typicality effects, dispensing the need to appeal
to any influence of local readings. We are sympathetic towards
\citeauthor{Tielvan-Tiel2012:Embedded-Scalar}'s innovative line of
reinterpretation of the data, but note, as
\citet{ChemlaSpector2010:Experimental-Ev} already observed, that his
typicality-based explanation does not extend to \es-sentences in an
obvious way\fn{For similar reasons, appeal to typicality cannot
  explain, as far as we can see, the
  preference for the situation in Figure~\ref{fig:literal-EA} over
  that in Figure\ref{fig:global-EA} given a sentence like
  (\ref{bsp:EA}).} and that it also does not explain why we observed putative
effects of typicality also in categorical judgements in our pilot.

\bigskip

To conclude, in order to decide about the availablity of local
implicatures we would ideally like to test situations that can
unambiguously be mapped to the different readings and do not differ in
typicality or other crucial properties. Given the logical dependencies
inherent to the relevant readings and the considerations concerning
typicality presented by van Tiel this seems impossible to achieve. As
we willl argue below we do, however, believe it is.

\begin{itemize}
\item what's needed
  \begin{itemize}
  \item evidence about all preferences
  \item factor out picture-complexity
  \item preferably categorical judgements
  \item intonation
  \end{itemize}

\end{itemize}

\bigskip

\begin{center}
  \textbf{Micha's notes:}
\end{center}

\begin{itemize}
\item K1:
  \begin{itemize}
  \item tried to replicate
    \citet{GeurtsPouscoulous2009:Embedded-Implic}'s study
  \item but tested all conditions
  \item used German cleft-sentences (possibly problematic)
  \item some evidence for subjective patterns in answers
  \end{itemize}
\item Thirdly, we observed that a tendency that participants
who rejected \as-sentences in the literal situation where more prone
to also accept \es-sentences in the local condition.\dn{spell out
  in appendix} This suggests that there might be participants who are
more likely to be influenced by local readings than others.
\end{itemize}

@@

  \caption{Distinguishing scenarios for sentence XYZ}
  \label{fig:EA-distinguishing-pics}

\subsection{To-Be-Included Here}
\label{sec:whats-missing}

\begin{itemize}
\item establish independence (as much as possible) of pictorial
  complexity/stereotypicality and assessment of reading
  \begin{itemize}
  \item not desirable to raise the level of relevance of local
    readings, because we want to test the base-line / default (cite
    Geurts / van Tiel)
  \item unclear what graded truth-value judgements measure exactly
    (re-read \citet{Chemla2009:Presuppositions} if needed)
  \item cannot separate judgements about sentences from judgements
    about pictures (van Tiel)
  \item unclear whether design assesses preferences of readings or
    targets pictorial complexity / typicality (van Tiel)
  \end{itemize}
\item provide a benchmark from which to deduce preference relations
\item control for intonational pattern (present auditorily)
  \begin{itemize}
  \item intonational effects discussed by
    \citet{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,Geurts2010:Quantity-Implic},
    \citep[c.f.][]{ChemlaSpector2010:Experimental-Ev}
  \item mention \citet{SchwarzClifton2008:Strengthening-o} (re-read,
    check for newer version)
  \end{itemize}
\item different languages
\end{itemize}

>>>>

\citet{ChemlaSpector2010:Experimental-Ev} also took issue with
\citeauthor{GeurtsPouscoulous2009:Embedded-Implic}'s design, arguing
that, firstly, the pictorial material used in
\citeauthor{GeurtsPouscoulous2009:Embedded-Implic}'s study was unduly
difficult; that, secondly, these pictures also may have failed to make
the local reading sufficiently relevant; and that, thirdly, the
restriction to a categorial choice (whether the sentence fits the
picture of not) may induce a bias against non-preferred readings in
cases where candidate readings stand in entailment relations
\citep[c.f.][for this latter
criticism]{Sauerland2010:Embedded-Implic}. To meet these potential
problems, \citet{ChemlaSpector2010:Experimental-Ev} presented subjects
with pictorial material like that in Figure~\ref{fig:Chemla-Spector},
which was assumed to be easier to assess and better at highlighting
the relevance of the local readings. Albeit in a different format, the
pictures used by \citeauthor{ChemlaSpector2010:Experimental-Ev} were
instantiations of the situation types in
Figures~\ref{fig:AS-distinguishing-pics} and
\ref{fig:ES-distinguishing-pics}. Additionally, subjects were asked,
not for categorial judgements, but for \mymark{graded judgements}:
subjects could freely click on a scale, as shown in
Figure~\ref{fig:Chemla-Spector}, to indicate how much they considered
a picture fitting for a given sentence \citep[c.f.][for more on this
method]{Chemla2009:Presuppositions}.

\begin{figure}[t]
  \centering

  \subfloat[][Example of the \as-weak condition of
  \citet{ChemlaSpector2010:Experimental-Ev}]{
      \label{fig:Chemla-Spector}
  \begin{minipage}{0.45\linewidth}
    \begin{center}
      \includegraphics[scale=0.25]{../pictures/paper/Chemla_Spector_2010_Critical_AE.png}\\
      \includegraphics[scale=0.25]{../pictures/paper/Chemla_Spector_2010_RatingBar.png}
    \end{center}

  \end{minipage}
    }
   \begin{minipage}{6cm}
     \subfloat[][Results \as-condition]{
    \label{fig:CS-Results-as}
        \includegraphics[width=5.5cm]{../pictures/paper/Chemla_Spector_2010_Results_AE.png}
  }

  \subfloat[test][Results \es-condition]{
    \label{fig:CS-Results-es}
    \includegraphics[width=5.5cm]{../pictures/paper/Chemla_Spector_2010_Results_GE.png}
  }  
   \end{minipage}
        \caption{Example trial and results of
          \citeauthor{ChemlaSpector2010:Experimental-Ev}'s
          (\citeyear{ChemlaSpector2010:Experimental-Ev}) study.}
\end{figure}

% \begin{figure}[t]
%   \centering
%       \includegraphics[scale=0.25]{../pictures/paper/Chemla_Spector_2010_Critical_AE.png}\\
%       \includegraphics[scale=0.25]{../pictures/paper/Chemla_Spector_2010_RatingBar.png}
%         \caption{Example of critical trial for \as-condition by
%           \citeauthor{ChemlaSpector2010:Experimental-Ev}'s
%           (\citeyear{ChemlaSpector2010:Experimental-Ev})}
%   \label{fig:Chemla-Spector}
% \end{figure}

\citeauthor{ChemlaSpector2010:Experimental-Ev} hypothesized that the
degree to which a sentence is rated acceptable is proportional to the
number of available true readings. Observed averaged clicking
positions are shown in Figures~\ref{fig:CS-Results-as} and
\ref{fig:CS-Results-es}.
%
% \begin{figure}
%   \centering
%   \subfloat[][\as-condition]{
%     \label{fig:CS-Results-as}
%         \includegraphics[width=5.5cm]{../pictures/paper/Chemla_Spector_2010_Results_AE.png}
%   }
%   \subfloat[test][\es-condition]{
%     \label{fig:CS-Results-es}
%     \includegraphics[width=5.5cm]{../pictures/paper/Chemla_Spector_2010_Results_GE.png}
%   }
%   \caption{Results from
%     \citeauthor{ChemlaSpector2010:Experimental-Ev}'s
%     (\citeyear{ChemlaSpector2010:Experimental-Ev}) study}
%   \label{fig:Chemla-Spector-Results}
% \end{figure}
%
According to \citeauthor{ChemlaSpector2010:Experimental-Ev}, the
crucial piece of evidence for the availability of local readings for
\as-sentences is that these sentences yielded higher graded
acceptability scores for the strong situation than for the weak
situation (although these differ only with respect to the truth value
of the local reading). In a similar way, evidence for the availability
of the local reading for \es-sentences comes from the difference
between the local and the literal situation. Strikingly, \es-sentences
received an average 73\% degree of acceptability in the local
situation although the literal and global readings are false in this
case.

@@

Summing up so far, three previous studies have presented different
pieces of evidence concerning putative local
readings. \citeauthor{ChemlaSpector2010:Experimental-Ev}'s results
suggest that local readings are not available, because they do not
affect a categorical truth-value judgments in a picture-verification
task. On the other hand,
\citeauthor{CliftonDube2010:Embedded-Implic}'s and
\citeauthor{ChemlaSpector2010:Experimental-Ev}'s design was suggested
to be sensitive enough to reveal effects of local readings: either by
a choice of the situation that better befits a given sentence
(\citeauthor{CliftonDube2010:Embedded-Implic}), or by a graded
truth-value judgment (\citeauthor{ChemlaSpector2010:Experimental-Ev}).

To account for all of these observations, it could be hypothesized
along with \citeauthor{CliftonDube2010:Embedded-Implic} and
\citeauthor{ChemlaSpector2010:Experimental-Ev} that local readings are
available, but so dispreferred that they do not affect simple
\emph{categorical} truth-value judgements. It could then furthermore
be argued, in line with traditionalism, that the reason why local
readings do not affect categorical judgements is because they are not
(strongly) truth-relevant speaker-intended meaning enrichments after
all, so that no case can be made for lexicalism or grammaticalism
\citep[c.f.][for arguments along these lines]{Tielvan-Tiel2012:Embedded-Scalar}.

Either position is cast into doubt by a pilot study of
ourselves.\dn{We should expand on the method in an appendix} We tried
to replicate \citeauthor{ChemlaSpector2010:Experimental-Ev}'s results,
using a simple categorial truth-value judgement task on pictures that
were exactly like those in Figures \ref{fig:AS-distinguishing-pics}
and \ref{fig:ES-distinguishing-pics}. Test sentences were German
cleft-constructions as in (\ref{bsp:AS-K1}) and
(\ref{bsp:ES-K1}).\fn{We concede that these cleft-constructions might
  unduly emphasize potential local readings, but that is not
  essential, because the main issue we are trying to address here is
  whether putative local readings \emph{could} affect categorical
  truth-value judgements.}
\begin{exe}
\ex \gll F\"{u}r \mymark{jedes} dieser Kinder gilt: es
  mag \mymark{einige} dieser Speisen. \label{bsp:AS-K1}\\
  For every {of these} children {it holds} it likes some {of
    these} dishes.\\
  For all of these children it holds that it likes some of these dishes.
\end{exe}
\begin{exe}
\ex \gll F\"{u}r \mymark{genau} \mymark{eines} dieser Kinder gilt: es
  mag \mymark{einige} dieser Speisen. \label{bsp:ES-K1}\\
  For exactly one {of these} children {it holds} it likes some {of
    these} dishes.\\
  For exactly one of these children it holds that it likes some of these dishes.
\end{exe}
Mean acceptance rates of 60 native German speakers for our target
sentences were:
\begin{center}
  \begin{tabular}{ccccccccc}
    \multicolumn{4}{c}{\as-sentences} &&
    \multicolumn{4}{c}{\es-sentences}     \\ \cmidrule(r){1-4} \cmidrule(r){6-9}
    false & literal & weak & strong && false & local & literal & all
    \\ \midrule 
    .9 & 72 & 79 & 90 && .8 & 20 & 71 & 93 
  \end{tabular}
\end{center}
Two observations are of interest here. Firstly, we observed 21\%
\emph{false}-judgements in the \as-weak condition, as well as 20\%
\emph{true}-judgements in the \es-local condition, contrary to the 0\%
in each case observed by
\citet{GeurtsPouscoulous2009:Embedded-Implic}. Secondly, the observed
difference between the \as-weak and the \as-strong conditions, on the
one had, and the \es-false and the \es-local condition, on the other
hand, both reached significance.\dn{spell out in appendix}

% \begin{figure}[]
% \centering
% \subfloat[\as-sentences]{
% \includegraphics[width=5.5cm]{../pictures/paper/JudgmentsAllSomeBars.pdf}
% \label{fig:EABars}
% }
% \subfloat[\es-sentences]{
% \includegraphics[width=5cm]{../pictures/paper/JudgmentsExactlySomeBars.pdf}
% \label{fig:EEBars}
% }
% \caption{Means of \emph{true}-judgments in our pilot study}
% \label{fig:Bars-K1}
% \end{figure}

These observed patterns suggest that local readings \emph{are}
available and \emph{can} have an effect even on categorical
truth-value judgements. However, this interpretation of the data is
problematic for reasons already addressed also by
\citet{ChemlaSpector2010:Experimental-Ev} and, more recently,
\citet{Tielvan-Tiel2012:Embedded-Scalar}. The problem is that the
present variants of truth-value judgment tasks all run risk of
conflating evidence about the availability or preference of readings
with properties of the pictorial material that are independent of the
reading to be assessed. This problem affects all of the studies
covered above, to some degree or other, because it follows almost
directly from the nature of the phenomenon under investigation and
therefore seems nearly impossible to avoid.

To illustrate the potential conflation, consider a sentence like
(\ref{bsp:EA}), which is a ``global alternative'' to an \es-sentence,
with a universal quantifier where an \es-sentence has scalar
\emph{some}.
\begin{exe}
\ex \gll F\"{u}r \mymark{genau} \mymark{eines} dieser Kinder gilt: es
  mag \mymark{jede} dieser Speisen. \label{bsp:EA}\\
  For exactly one {of these} children {it holds} it likes all {of
    these} dishes.\\
  For exactly one of these children it holds that it likes all of these dishes.
\end{exe}
Sentences like (\ref{bsp:EA}) are literally true in both of the
situations in Figure~\ref{fig:EA-distinguishing-pics}, but these
situations differ in the truth value of the corresponding
\es-sentence.
%
\begin{figure}[]
  \centering

@@

\caption{Distinguishing scenarios for sentence(\ref{bsp:EA})}
  \label{fig:EA-distinguishing-pics}

\end{figure}
%
Our pilot study revealed a difference in acceptability,
but a curious one. The sentence was judged \emph{true} in 90.3\% of
the cases for the situation in Figure~\ref{fig:global-EA} and in
98.3\% in situation \ref{fig:literal-EA}. The observed difference is
significant ($t = -3.8259$, $df = 322.375$, $p < 0.001$). This is a
curious finding, because, from the point of view of implicature
calculation, the only thing that could plausibly explain this
acceptability difference is the presence of a global implicature,
resulting from the negation of the corresponding
\es-sentence.\fn{Notice that (\ref{bsp:EA}) is the alternative to the
  corresponding \es-sentence needed for computing the putative global
  implicature. But these sentences are logically independent. So, it
  may be that the corresponding \es-sentence is an alternative also to
  sentences like (\ref{bsp:EA}). It may also be that being an
  alternative is not a symmetric notion. Be that as it may, our
  argument does not hinge on whether (\ref{bsp:EA}) does or does not
  actually have a global implicature of the alleged kind.} But such a
putative global implicature would be true in the
situation~\ref{fig:global-EA}, but false in the
situation~\ref{fig:literal-EA}. Consequently, the observed difference
in acceptability cannot be explained simply in terms of the hypothesis
of \citet{ChemlaSpector2010:Experimental-Ev} that acceptability is
proportional to the number of available true readings. Rather some
feature of the pictorial material that is independent of the putative
readings under scrutiny does affect truth-value judgements, even
categorical ones.

\citet{ChemlaSpector2010:Experimental-Ev} acknowledge the possibility
that the \emph{typicality} of a picture may affect graded truth-value
judgements. Stronger still, they show that graded judgments of
\as-sentences differ significantly for different instantiations of the
conditions in \ref{fig:AS-distinguishing-pics}, that vary in the
amount of connections without changing the assignment of truth values
to candidate readings. \citeauthor{ChemlaSpector2010:Experimental-Ev}
suggest that typicality of the pictorial material can account for
these differences, but submit that this does not explain away the
effect of the local reading. This is disputed by
\citet{Tielvan-Tiel2012:Embedded-Scalar}, who demonstrates that all of
\citeauthor{CliftonDube2010:Embedded-Implic}'s and
\citeauthor{ChemlaSpector2010:Experimental-Ev}'s data on \as-sentences
can be explained as typicality effects, dispensing the need to appeal
to any influence of local readings. We are sympathetic towards
\citeauthor{Tielvan-Tiel2012:Embedded-Scalar}'s innovative line of
reinterpretation of the data, but note, as
\citet{ChemlaSpector2010:Experimental-Ev} already observed, that his
typicality-based explanation does not extend to \es-sentences in an
obvious way\fn{For similar reasons, appeal to typicality cannot
  explain, as far as we can see, the preference for the situation in
  Figure~\ref{fig:literal-EA} over that in Figure\ref{fig:global-EA}
  given a sentence like (\ref{bsp:EA}).} and that it also does not
explain why we observed putative effects of typicality also in
categorical judgements in our pilot.

To conclude, the confounding effects of pictorial complexity and/or
typicality are real and affect even categorical judgements. The
available evidence about availability, preference and nature of local
readings is therefore still inconclusive. What is needed to complement
the picture is data from a design that elicits categorical judgements
that are as independent as possible of possibly conflating properties
of the pictorial material. Given the logical dependencies of the
relevant readings of \as- and \es-sentences this seems almost
impossible to achieve. As we will argue below we do, however, believe
it is.

On top of this, we would like to obtain more further information about
the relative preferences among all putative readings, so as to be able
to decide between theoretical positions, as outlined in
Section~\ref{sec:theories-predictions}. Neither of the previous
studies gives us that, either because they simply have not
investigated all the relevant comparisons
(\citet{GeurtsPouscoulous2009:Embedded-Implic},
\citet{CliftonDube2010:Embedded-Implic}), or because they cannot safely
derive the required cardinal information for danger of conflating
preferences for readings with preferences for pictures
(\citet{ChemlaSpector2010:Experimental-Ev}, our pilot study).

Another desideratum for a further empirical testing is that a study
aimed at revealing information about availability and preferences of
readings be accompanied by a suitable comparable investigation into a
phenomenon which is know to allow for several readings with a given
known preferences structure. This way and only this way can a proper
baseline be established to guide the interpretation of the observed
data.

Moreover, a final omission of previous studies is that they did not
control for possible conflating effects of ``silent intonation''
(XYZ)\dn{references}. Even traditionalism maintains that local
readings are attested, but requiring a contrastive stress on the
scalar item
\citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,Geurts2010:Quantity-Implic,Tielvan-Tiel2012:Embedded-Scalar}. Variation
in the interpretation of target sentences therefore could be caused by
subjects imposing different intonational patterns on the visually
presented target sentences. Ideally, we should therefore present
sentences auditorily and address directly the frequently voiced
hypothesis that local readings are triggered by contrastive
stress.\dn{relate to \citet{SchwarzClifton2008:Strengthening-o} and
  others?}

The following section presents a study designed to meet all of these
desiderata.
